### 2022-02-24 paper/localpsf.tex
local mean displacement section of paper written. reads well

Let $x$ and $x'$ be points in $\Omega$ that are close to each other, and consider the following three approximations:
\begin{align}
	\phi_x(y) &\approx \phi_{x'}(y) \label{eq:translate1}\\
	\phi_x(y) &\approx \phi_{x'}(y-x+x') \label{eq:translate2}\\
	\phi_x(y) &\approx \phi_{x'}\left(y-\mu(x)+\mu(x')\right). \label{eq:translate3}
\end{align}
These approximations are illustrated in Figure FIG.

Operators satisfying \eqref{eq:translate1} can be well-approximated via low-rank interpolative factorization of the kernel $\Phi$.
% of the form
%\begin{equation}
%	\label{eq:low_rank_interpolation}
%	\Phi(y,x) \approx \sum_{i=1}^r w_i(x) \phi_{x_i}(y)
%\end{equation}
%where $\phi_{x_i}$ are known impulse responses at a collection of points $x_i$ scattered throughout $\Omega$, and $w_i$ are smooth weighting functions that interpolate the $\phi_{x_i}$. 
However, such approximations are not suitable if $\Aop$ is high rank.
%, such as Hessians in inverse problems with highly informative data. 
%Moreover, if $\Aop$ is numerically low rank, then one would typically use more accurate and robust matrix-free methods for forming low-rank approximations, such as randomized SVD or Lanczos.
Operators that satisfy \eqref{eq:translate2} are called ``locally translation-invariant'' because integral kernel entries $\Phi(y,x)$ for such operators are approximately invariant under translation of $x$ and $y$ by the same displacement, i.e., $x \rightarrow x+h$ and $y \rightarrow y+h$. Locally translation-invariant operators act like convolutions locally, and can therefore be well-approximated by so-called product-convolution approximations---weighted sums of convolution operators with spatially varying weights. Product-convolution approximations can be high-rank even if the number of convolution operators used in the approximation is small.

>>>>

Let $x$ and $x'$ be points in $\Omega$ that are close to each other, and consider the following three approximations:
\begin{align}
	\phi_x(y) &\approx \phi_{x'}(y) \label{eq:translate1}\\
	\phi_x(y) &\approx \phi_{x'}(y-x+x') \label{eq:translate2}\\
	\phi_x(y) &\approx \phi_{x'}\left(y-\mu(x)+\mu(x')\right). \label{eq:translate3}
\end{align}
Approximations \eqref{eq:translate1} and \eqref{eq:translate2} are standard. Approximation \eqref{eq:translate3}, which we use,  is new. These approximations are illustrated in Figure FIG.

Approximation \eqref{eq:translate1} follows from a smoothness assumption on the kernel $\Phi$. Operators satisfying \eqref{eq:translate1} can be well-approximated via low-rank interpolative factorization of the kernel $\Phi$.
% of the form
%\begin{equation}
%	\label{eq:low_rank_interpolation}
%	\Phi(y,x) \approx \sum_{i=1}^r w_i(x) \phi_{x_i}(y)
%\end{equation}
%where $\phi_{x_i}$ are known impulse responses at a collection of points $x_i$ scattered throughout $\Omega$, and $w_i$ are smooth weighting functions that interpolate the $\phi_{x_i}$. 
However, such approximations are not suitable if $\Aop$ is high rank.
%, such as Hessians in inverse problems with highly informative data. 
%Moreover, if $\Aop$ is numerically low rank, then one would typically use more accurate and robust matrix-free methods for forming low-rank approximations, such as randomized SVD or Lanczos.
Operators that satisfy \eqref{eq:translate2} are called ``locally translation-invariant'' because integral kernel entries $\Phi(y,x)$ for such operators are approximately invariant under translation of $x$ and $y$ by the same displacement, i.e., $x \rightarrow x+h$ and $y \rightarrow y+h$. Locally translation-invariant operators act like convolutions locally, and can therefore be well-approximated by so-called product-convolution approximations---weighted sums of convolution operators with spatially varying weights. Product-convolution approximations can be high-rank even if the number of convolution operators used in the approximation is small.
